A Wait-Free Queue with Polylogarithmic Step Complexity

### 2023-06-12 presentation/podc-presentation.tex
x
added slide about ordering tree

\newcommand{\Red}[1]{{\color{red}#1}}
\newcommand{\Blue}[1]{{\color{blue}#1}}
\newcommand{\Green}[1]{{\color{green}#1}}

@@

>>>>

\newcommand{\Red}[1]{{\color{red}#1}}
\newcommand{\Blue}[1]{{\color{blue}#1}}
\newcommand{\Green}[1]{{\color{green}#1}}
\newcommand{\Purple}[1]{{\color{violet}#1}}

@@

\begin{frame}{Ordering Tree}
\visible<5>{\hfill Use ordering in root as linearization\hfill}
\medskip

\only<1>{\input{OrderTree-50.pdf_t}}%
\only<2>{\input{OrderTree-50to51.pdf_t}}%
\only<3>{\input{OrderTree-50to52.pdf_t}}%
\only<4->{\input{OrderTree-50to53.pdf_t}}

\begin{frame}{Propagating Operations to the Root}

\begin{enumerate}
\item
Append operation to your leaf
\item
At each node $v$ on path to root refresh {\it twice}:
\begin{enumerate}[(a)]
\item
Read unpropagated operations in both of $v$'s children
\item
CAS them into $v$
\end{enumerate}
\end{enumerate}

\pause
\medskip

Double Refresh:\\
If your CAS on $v$ fails twice, then\\
another process has propagated your operation to $v$.

\pause
\medskip
Avoids CAS retry problem.
\end{frame}

\begin{frame}{Main Challenge}

Refresh may have to propagate up to $p$ operations\\
$\Rightarrow$ need an \Red{implicit representation}
